\documentclass[10pt]{article}

\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[backend=biber,style=verbose,maxbibnames=99,maxcitenames=99]{biblatex}
\usepackage{comment}
\bibliography{moyer.bib}
\renewcommand{\labelitemi}{}

\makeatother

\hypersetup{colorlinks,%
  citecolor=black,%
  filecolor=black,%
  linkcolor=black,%
  urlcolor=black,%
  pdftex} \usepackage{fullpage} \textheight=9.0in \pagestyle{plain}
\raggedbottom \raggedright \setlength{\tabcolsep}{0in}
\hyphenpenalty=10000

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
  \multicolumn{2}{c}{\LARGE{\textbf{THOMAS MOYER}}}
  \vspace{1em}\\ 
  333G Woodward Hall\\
  University of North Carolina at Charlotte & \href{mailto:tom.moyer@uncc.edu}{tom.moyer@uncc.edu}\\
  9201 University City Blvd. & (704) 687-8194 \\
  Charlotte, NC 28223
  \\
\end{tabular*}
\\
\vspace{0.1in} 
\hypertarget{education}{%
\section*{Education}\label{education}}
\addcontentsline{toc}{section}{education}
%{\Large \textbf{EDUCATION}}

\begin{itemize}
\tightlist
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    \href{http://www.psu.edu}{\textbf{The Pennsylvania State University}} & University Park, PA \\
    PhD, Computer Science and Engineering, December 2011 & \\
    Advisor: \href{http://www.patrickmcdaniel.org}{Dr. Patrick D. McDaniel} & \\
    Dissertation Title: \em{Building Scalable Document Integrity Systems} & %\\
  \end{tabular*}

\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    \href{http://www.psu.edu}{\textbf{The Pennsylvania State University}} & University Park, PA \\
    MS, Computer Science and Engineering, 2009 & \\
    Advisor: \href{http://www.patrickmcdaniel.org}{Dr. Patrick D. McDaniel} & \\
    Thesis Title: \em{Scalable Web Content Attestations} & %\\
  \end{tabular*}

\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    \href{http://www.psu.edu}{\textbf{The Pennsylvania State University}} & University Park, PA \\
    B.S., Computer Engineering, 2006 & 
  \end{tabular*}

\end{itemize}

%\vspace{1em} {\Large \textbf{ACADEMIC APPOINTMENTS}}
\hypertarget{academic-appointments}{%
\section*{Academic Appointments}\label{academic-appointments}}
\addcontentsline{toc}{section}{academic-appointments}
\begin{itemize}
\tightlist
\item \textbf{Assistant Professor}, August 2017-present\\
  \textit{University of North Carolina at Charlotte},\\
  \textit{Department of Software and Information Systems}\\
  Charlotte, NC\\

\item \textbf{Research Assistant}, Summer 2008 to Fall 2011\\
  \textit{The Pennsylvania State University},
  University Park, PA\\
  Advisor: Dr. Patrick D. McDaniel\\
  Worked on problems in virtual machine security.\\
  Utilized technologies for virtualization and trusted hardware to develop secure computing applications.\\
  Worked on problems in Web security.

\item \textbf{Research Assistant}, Fall 2007 to Spring 2008\\
  \textit{The Pennsylvania State University},
  University Park, PA\\
  Advisor: Dr. Patrick D. McDaniel\\
  Mentor: Dr. Subhabrata Sen\\
  Worked on problems in configuration management.\\
  Assisted in developing/testing tool for creating router configurations.

\item \textbf{Instructor}, Spring 2007\\
  \textit{The Pennsylvania State University},
  University Park, PA\\
  Department of Computer Science Engineering, Pennsylvania State University\\
  Introduction to Algorithmic Processes (CMPSC 101)\\
  Instructed students in program design and creation using the MS Visual Basic programming language.
\end{itemize}


%\vspace{1em} {\Large \textbf{INDUSTRIAL APPOINTMENTS}}
\hypertarget{industrial-appointments}{%
\section*{Industrial Appointments}\label{industrial-appointments}}
\addcontentsline{toc}{section}{industrial-appointments}
\begin{itemize}
\item \textbf{Research Scientist}, Fall 2011 to Summer 2017\\
  \textit{Cyber Systems and Technology Group}, MIT Lincoln Laboratory, Lexington, MA\\
  Worked on secure system design and prototyping.\\
  Developed prototype for protected, mobile, satellite communications terminal, including addressing information assurance requirements for multiple organizations.\\
  Developed understanding of certification and accreditation processes used to certify information systems.\\
  Participated in blue-team threat assessment for legacy computer systems.\\
  Supported DoD ASD(R\&E) Information Systems and Cyber Technologies office as subject matter expert in cyber security.\\
  Developed secure data provenance architectures for large-scale enterprise systems.\\
  
\item \textbf{Summer Research Intern AT\&T}, Summer 2007\\
  \textit{Internet and Networking Systems Research Center}, AT\&T Labs
  Research,
  Florham Park, NJ\\
  Mentor: Dr. Subhabrata Sen\\
  Worked on problems in configuration management.\\
  Assisted in developing internal tool for creating configurations.

\item \textbf{Systems Administrator}, Spring 2004 to Summer 2007\\
  \textit{Geodynamics Research Group}, The Pennsylvania State University,
  University Park, PA\\
  Supervised by Dr. Kevin Furlong\\
  Responsible for maintaining and upgrading systems and
  infrastructure.\\
  Implemented an automated, platform independent, remote backup
  system.\\
  Assisted with some minimal scientific programming for research.
\end{itemize}

\input{activities}

\hypertarget{publications}{%
\section*{Publications}\label{publications}}
\addcontentsline{toc}{section}{publications}
%\vspace{1em} {\Large \textbf{PUBLICATIONS}}\\
\input{pubs}

\end{document}