\documentclass[10pt]{article}

\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[backend=biber,style=verbose,maxbibnames=99,maxcitenames=99]{biblatex}
\usepackage{comment}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{totpages}
\usepackage{etoolbox}
\usepackage{framed}

\newenvironment{quotationb}%
{\begin{leftbar}\begin{quotation}}%
{\end{quotation}\end{leftbar}}

\newtoggle{REVIEW}
\togglefalse{REVIEW}
%\toggletrue{REVIEW}

\hypersetup{colorlinks,%
  citecolor=black,%
  filecolor=black,%
  linkcolor=black,%
  urlcolor=black}

%\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\hyphenpenalty=10000

\pagestyle{fancy}
\fancyhead[C]{Thomas Moyer}
\fancyhead[L,R]{}
\fancyfoot[C]{Curriculum Vitae}
\fancyfoot[L]{February 2021}
\fancyfoot[R]{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.4pt}
\setlength{\parskip}{0.65em}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0.25em}}

\addbibresource{moyer.bib}

\begin{document}
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
  \multicolumn{2}{c}{\Large{\textsc{Curriculum Vitae}}}
  \vspace{1em}\\ 
  Thomas Moyer\\
  177 Bromley Village Drive, Unit 201 &  \href{mailto:tommoyer@gmail.com}{tommoyer@gmail.comu}\\
  Fort Mill, SC 29708 & (814) 933-8135
  \\
\end{tabular*}
\\

\vspace{0.1in} 
\hypertarget{education}{%
\section{Education}\label{education}}

\renewcommand{\labelitemi}{}
\begin{itemize}
\tightlist
\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    \href{http://www.psu.edu}{\textbf{The Pennsylvania State University}} & University Park, PA \\
    PhD, Computer Science and Engineering, December 2011 & \\
    Advisor: \href{http://www.patrickmcdaniel.org}{Dr. Patrick D. McDaniel} & \\
    Dissertation Title: \em{Building Scalable Document Integrity Systems} & %\\
  \end{tabular*}

\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    \href{http://www.psu.edu}{\textbf{The Pennsylvania State University}} & University Park, PA \\
    MS, Computer Science and Engineering, 2009 & \\
    Advisor: \href{http://www.patrickmcdaniel.org}{Dr. Patrick D. McDaniel} & \\
    Thesis Title: \em{Scalable Web Content Attestations} & %\\
  \end{tabular*}

\item
  \begin{tabular*}{6in}{l@{\extracolsep{\fill}}r}
    \href{http://www.psu.edu}{\textbf{The Pennsylvania State University}} & University Park, PA \\
    B.S., Computer Engineering, 2006 & 
  \end{tabular*}

\end{itemize}
\renewcommand{\labelitemi}{\textbullet}

\hypertarget{professional-experience}{%
\section{Professional Experience}\label{professional-experience}}

\begin{itemize}
\tightlist
\item \textbf{Assistant Professor}, August 2017-present\\
  University of North Carolina at Charlotte\\
  Department of Software and Information Systems\\
  Charlotte, NC\\
  \textit{
Conducted research on a number of related areas: 1) novel solutions for building resilient systems that ensured continued operation in the face of compromise; 2) secure software-defined networking to support resilient systems; 3) trustworthy endpoint agent designs. Developed architectures that aimed to be efficient and secure against advanced adversaries. Techniques explored included data provenance and graph analysis. Target systems included cloud, enterprise, and embedded systems.\\
\mbox{}\\
Developed and taught two classes. The first was titled IT Infrastructure and Security where students learned about the configuration and management of enterprise services (e.g., DNS, LDAP, Kerberos, network storage, email servers, and web servers). I restructured the class to introduce containers and virtualization into the curriculum and integrated each of the assignments culminating in a functioning email server for a small enterprise network. The second class was titled Competitive Cyber Defense, an advanced undergraduate and graduate class, where students examined techniques for building secure architectures for enterprise services. In this class students would develop a plan to secure an existing enterprise network, including system and network security policies.
\mbox{}\\
Served as a mentor for several PhD, MS, and undergraduate student projects, helping students develop technical and professional skills. Helped with issues surrounding career path selection, technical skill development, and professional skill development. Additionally, I established a research lab within the university focused on research into resilient systems. In this lab, students worked collaboratively on research projects under my supervision.
\mbox{}\\
Acted as faculty mentor for the 49th Security Division, a student organization that focused on cybersecurity and ethical hacking. As part of this role, I helped students prepare for cybersecurity competitions such as the National Collegiate Cyber Defense Competition and the Department of Energy Cyberforce competition.}

\item \textbf{Research Scientist}, September 2011 to August 2017\\
  \textbf{Secure Resilient Systems and Technology Group}, MIT Lincoln Laboratory, Lexington, MA\\
\textit{
Principal investigator and designer of the security architecture for a mobile satellite communications terminal. Created a novel security architecture that met the security and information assurance requirements of the funding agency. The architecture relied on Linux-based virtualization and trusted computing hardware (i.e. the Trusted Platform Module) to ensure the integrity and confidentiality of the data and code for the platform.\\
\mbox{}\\
Worked on several programs related to cloud computing security and data provenance, including a program to integrate data provenance into applications that would ensure the integrity of the data being used to make decisions. The data provenance system included an analytic framework that would alert end-users to issues related to the data being accessed. Developed a lightweight data provenance collection system that could be integrated into existing security architectures where information assurance accreditation was required.\\
\mbox{}\\
Served as a technical advisor to the Department of Defense within the office of the Assistant Secretary of Defense for Research and Engineering. Evaluated research programs and proposals and provided guidance on future directions for program investments.}

\item \textbf{Research Assistant}, May 2008 to September 2011\\
  The Pennsylvania State University\\
  University Park, PA\\
  Advisor: Dr. Patrick D. McDaniel\\
  \textit{Studied and developed systems to support integrity of web content protected by the Trusted Platform Module. Developed efficient solutions to certify the integrity of content, ensuring a minimal reduction in throughput while providing stronger security guarantees about the content being served. Explored solutions for secure storage architectures as part of a collaborative project. Developed solutions to demonstrate novel security solutions based on upcoming storage architectures.}

\item \textbf{Research Assistant}, September 2007 to May 2008\\
  The Pennsylvania State University
  University Park, PA\\
  Advisor: Dr. Patrick D. McDaniel\\
  Mentor: Dr. Subhabrata Sen\\
  \textit{ Worked on problems in configuration management. Assisted in developing/testing tool for creating router configurations.}

\item \textbf{Summer Research Intern AT\&T}, May 2007 to September 2007\\
  Internet and Networking Systems Research Center, AT\&T Labs Research,\\
  Florham Park, NJ\\
  Mentor: Dr. Subhabrata Sen\\
  \textit{Worked on problems in configuration management. Assisted in developing internal tool for creating configurations.}

\item \textbf{Instructor}, January 2007 to May 2007\\
  The Pennsylvania State University\\
  University Park, PA\\
  Department of Computer Science Engineering, Pennsylvania State University\\
  \textit{Taught Introduction to Algorithmic Processes (CMPSC 101). Instructed students in program design and creation using the MS Visual Basic programming language.}

\end{itemize}

\hypertarget{skills-and-experience}{%
\section{Selected Skills and Technology Experience}\label{skills-and-experience}}
\textit{Ordered by experience}
\begin{itemize}
\tightlist
\item \textbf{Programming languages:} Python, C, Bash, Java, C++, Ruby
\item \textbf{Linux system administration:} automation, management, deployment, kernel programming
\item \textbf{Security:} public-key cryptography, mandatory access control policies (SELinux and AppArmor), firewall administration and policy development
\item \textbf{Cloud technology:} Virtualization, Containers (LXC, LXD, Docker), Proxmox Virtual Environment, VMware ESXi and vSphere

\end{itemize}

%\hypertarget{licenses-and-certifications}{%
%\section{Licenses and Certifications}\label{licenses-and-certifications}}
%\addcontentsline{toc}{section}{licenses-and-certifications}

\iftoggle{REVIEW}{
  \hypertarget{career-highlights}{%
  \section{Career Highlights}\label{career-highlights}}
  \input{highlights}
}

\hypertarget{publications}{%
\section{Publications}\label{publications}}
\input{publications}

\iftoggle{REVIEW}{
  \hypertarget{funding}{%
  \section{Extramural Funding}\label{funding}}
  \input{funding}
}

\hypertarget{students}{%
\section{Student Supervision}\label{students}}
\input{students}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\iftoggle{REVIEW}{
  \input{teaching-accomp}
}
\input{teaching}

\hypertarget{service}{%
\section{Service and Outreach}\label{service}}
\iftoggle{REVIEW}{
  \input{service-accomp}
}
\input{service-external}
\iftoggle{REVIEW}{
  \input{service-panels}
  \input{service-internal}
}
\iftoggle{REVIEW}{
  \input{leadership}
  \input{research-stmt}
  \input{teaching-stmt}
  \input{peers}
  \input{venues}
}

\end{document}